\documentclass[a4paper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
\newcommand\skills{ 
\vspace*{-0.1cm}
~
	\smartdiagram[bubble diagram]{
        \textbf{Micro}\\\textbf{Engineering},
        \textbf{~~~    Photonics~~~}, %\\\textbf{Web Dev},
        \textbf{~Micro/Nano~}\\\textbf{Systems},
        \textbf{~~Electronics~~}\\\textbf{\& EDA},
        \textbf{Mechanics \&}\\\textbf{Design (CAD)},
        \textbf{~~~~~~Prog-~~~~~~}\\\textbf{ramming},
        \textbf{Embedded}\\\textbf{Systems-IoT}
    }
\vspace*{-0.4cm}
}

% Programming skill bars
\programming{
{
    \hspace{-0.15cm}OpticStudio $\bullet$ Adobe CS  $\bullet$ \large \LaTeX / 3
}, 
{
    \hspace{-0.15cm}HTML|CSS|PHP|SQL $\bullet$ Assembly / 4
}, 
{
    \hspace{-0.15cm}Mathematica $\bullet$ MS Office $\bullet$ Java  / 5
},
{
    \hspace{-0.15cm}Catia $\bullet$ Eagle $\bullet$ C\# $\bullet$ Quartus|FPGA / 5.5
},
{
    \hspace{-0.15cm}Matlab $\bullet$ EasyEDA $\bullet$ C|C++ $\bullet$ Python/ 6
}}

% Projects text
\projects{
        \textbf{Nationality} - Swiss \\
        \textbf{Born on the} 11/03/1996  - \textbf{23 y. o.}\\
        \textbf{Civil registration} - Bachelor \\
        \textbf{Adress} - ch. des Plantaz 12, 1180 Rolle
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}
\cvname{Frédéric} % Your name
\cvjobtitle{ de Goumoëns } % Job
\cvjobtitlebis{ Microengineering - EPFL\\} % Job
% title/career

\cvlinkedin{/in/fdegoumo}

\cvnumberphone{+41 (0)78 631 89 89} % Phone number

\cvmail{fdeg@bluewin.ch} % Email address

%----------------------------------------------------------------------------------------

\usepackage[nopar]{lipsum}

\begin{document}
\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\hfill \scalebox{1.2}{\href{http://fdeg.ch/CV}{\textbf{\textcolor{gray}{fdeg.ch}\textcolor{pblue}{/CV }}\mpoint}} 
\vspace*{-0.3cm}
\section{Education}
\vspace*{-0.1cm}

\begin{twenty} % Environment for a list with descriptions
    %%
    %%\twentyitem
    %%	{2020}
    %%    {}
    %%    {Master's Thesis in Photonics at Caltech}
    %%    {\href{https://www.caltech.edu/}{California Institute of Technology}}
    %%    {}
    %%    {Developing a wavefront shaping device in the Biophotonics Lab}
    %%\\
    \twentyitem
    	{2020}
        {2018}
        {Master's Student in Microengineering \textnormal{(Aver.: 5.75/6)}}
        {\href{https://www.epfl.ch/education/master/programs/microengineering/}{EPFL}}
        {
        Minor in Photonics with a focus on Embedded Systems, Machine Learning, Image Processing, Nanotechnology and Product Design.\\\null\hfill\href{http://fdeg.ch/CV/EPFL_Results/Master_Statement_of_Results.pdf}{\textbf{Master's courses \& Statement of results \mpoint}} 
        }
        {}
	\twentyitem
    	{2017}
        {2014}
        {BSc., Microengineering \textnormal{(Aver.: 5/6)}}
        {\href{https://bachelor.epfl.ch/microtechnique}{EPFL}}
        {
        Electrical \& Mechanical Eng., Computer Science, Microfabrication.\\\null\hfill\href{http://fdeg.ch/CV/EPFL_Results/Bachelor_Statement_of_Results.pdf}{\textbf{Bachelor's courses \& Statement of results \mpoint}}
        }
        {}
    \twentyitem
    	{2014}
        {2011}
        {Maturity Diploma \textnormal{(Aver.: 5/6)}}
        {\href{https://www.gymnase-morges.ch/}{Gymnase de Morges}}
        {
        Math/Physics and Computer science.
        }
        {}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace*{-0.3cm}
\section{Experience}
\vspace*{-0.1cm}

\begin{twenty} % Environment for a list with descriptions
    \twentyitem
    	{Dec 2019}
		{Avr 2019}
        {Chief Electronic Designer}
        {\href{https://www.ouay.ch/}{Ouay}}
        {Development of the cellular communication, embedded sensors and powering of the new device intended for the elderly.}
        {}
    \twentyitem
    	{Avr 2019}
		{Jun 2018}
        {Intern at LEDsafari, Hardware developer}
        {\href{http://ledsafari.com/remote-monitoring/}{LEDsafari}}
        {
        R\&D and manufacturing of a product for remote monitoring of solar panels. A patent and a  \href{https://www.smarthelio.com/}{\textbf{startup}} came out from this product.
        }
        {}
    \twentyitem
    	{Nov 2017}
		{Jul 2017}
        {Military service}
        {\href{https://www.vtg.admin.ch/fr/moyens-d-engagement/boden-luft/stinger.html}{Swiss Army}}
        {
        Basic training, anti-aircraft soldier (STINGER).
        }
        {}
	\twentyitem
    	{Jul 2017}
		{Feb 2017}
        {Teaching assistant in Analysis IV}
        {\href{http://edu.epfl.ch/coursebook/fr/analyse-iv-MATH-207-D}{Math section - EPFL}}
        {
        Tutoring and supervision of tutorial sessions for second year engineering students for advanced analysis courses. \hfill
        \href{http://fdeg.ch/Reports/Coursebook_Analyse_IV.pdf}{\textbf{Coursebook \mpoint}}
        }
        {}
    \twentyitem
   		{Aug 2016}
		{Jul 2016}
        {Machine Shop Internship}
        {\href{https://www.etml.ch/}{ETML}}
        {Training in the fields of design and production. \hfill
        \href{http://fdeg.ch/Reports/ETML_Machine_Shop.pdf}{\textbf{Report \mpoint}} 
        }
        {}
    
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

\vspace*{-0.3cm}
\section{Projects}
\vspace*{-0.1cm}

\begin{twenty} % Environment for a list with descriptions
    \twentyitem
    	{Dec 2019}
		{Sep 2019}
        {Machine vision microfluidics for single-cell analysis}
        {\href{https://deplanckelab.epfl.ch}{Deplancke - EPFL}}
        {
        Development of an embedded computer vision platform for high-performance cell detection and hardware accelerated image processing. Creation of a python GUI to control the FPGA board.}
        {}
     \twentyitem
    	{Jun 2019}
		{Feb 2019}
        {Laser-based needle-free injection device}
        {\href{https://lapd.epfl.ch/}{LAPD - EPFL}}
        {
        Development of a new solution using optical fibers and microfluidics for needle-free injection into biological tissue in a minimally invasive device. \hfill
        \href{http://fdeg.ch/Reports/LAPD_Report.pdf}{\textbf{Report \mpoint}}  
        }
        {}
    \twentyitem
    	{Jun 2019}
		{Feb 2019}
        {\textcolor{pblue}{P}etch\hspace{0.2mm}\textcolor{pblue}{\scalebox{1.2}{i}}t - Ball thrower for dogs}
        {\href{https://edu.epfl.ch/coursebook/en/products-design-systems-engineering-MICRO-406}{Products design \& systems engineering}}
        {
        Creation of an innovative ball thrower intended for persons with reduced mobility wishing to play with their dog.\hfill
        \href{http://fdeg.ch/Reports/PetchIt_Report.pdf}{\textbf{Report}} \textbf{|}
        \href{https://www.youtube.com/watch?v=D7fW0_doyIM&list=PLYHF3kEHYpgcjWwVfPJ-mZfmi9ZN5I3l9}{\textbf{Video}} \mpoint
        }
        {}
    \twentyitem
    	{Dec 2019}
		{Mar 2017}
        {CleverCockpit - Aircraft navigation assistant}
        {\href{http://www.aeroformation.ch/Bienvenue.html}{AeroFormation}}
        {
        Making of a cheap commercial product for assisting private planes' pilots. Consists of a low consumption battery powered e-Paper display and customizable sensors.\hfill \href{http://clevercockpit.ch/}{\textbf{Product Website \mpoint}}
        }
        {}
        \\
    %\twentyitem
   	%	{Jun 2017}
	%	{Feb 2017}
    %   {Robot programming, audio signal processing}
    %  {\href{http://sti.epfl.ch/microtechnique}{SMT - EPFL}}
    %    {}
    %    {
    %    {Control of the "e-puck" robot (DsPIC processor) %using frequency analysis of received sounds (assembly, %C, Matlab). Making of a Windows app as a sound %controller (C\#).%. Sous la supervision du Prof. R. %Boulic
    %    }
    %    }
    %\\   
    %
    %\twentyitem
   	%	{Feb 2016 -}
	%	{Jun 2016}
    %    {Linear guidance by flexible elements}
    %    {\href{http://sti.epfl.ch/microtechnique}{SMT - EPFL}}
    %    {}
    %    {
    %    {Design of a mechanism able to guide a unit during a vertical movement in a perfectly rectilinear way using flexible joints %Sous la supervision du Prof. S. Henein
    %    }
    %    }
    %\\
\end{twenty}

\vspace{-0.8cm}
\section{Languages}
\vspace{-0.1cm}
\begin{twenty} % Environment for a list with descriptions
	\vspace{-0.3cm}
	\twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{French}}}}
        {}
        {\textnormal{Mother tongue}}
        {}
        {}
        {}
    \vspace{-0.3cm}
    \twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{German}}}}
        {}
        {\textnormal{B2 Certificate, limited professional skills}}
        {}
        {}
        {}
	\twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{English}}}}
        {}
        {\textnormal{B2 Certificate, professional skills}}
        {}
        {}
        {}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

\vspace{-0.4cm}
\section{Hobbies}
\vspace{-0.1cm}
\begin{twenty} % Environment for a list with descriptions
    \vspace{-0.3cm}
    \twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{Sport}}}}
        {}
        {\textnormal{Circus, Diabolo, Badminton, Skiing, Biking, Sailing, Judo \hfill\href{https://www.youtube.com/watch?v=k7dW7igYiwI&list=PLYHF3kEHYpgf9jwPGn_NW_Ha0ea9cQ2uj}{\textbf{Videos \mpoint}}}}
        {}
        {}
        {}
    \vspace{-0.3cm}
	\twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{DIY}}}}
        {}
        {\textnormal{3D Printng, Machining, Microcontrollers, PCB, Welding, Assembly}}
        {}
        {}
        {}
    \twentyitem
    	{\textnormal{\textbf{\scalebox{1.1}{Video}}}}
        {}
        {\textnormal{Aerial drone footage, Filming, Video editing}}
        {}
        {}
        {}
%Répétiteur de maths et informatique, Moniteur camp aviation (2016)\Juggling, Diabolo, Acrobatics, Performing

	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}
\clearpage
\end{document} 


